Quality Metrics for SKOS Vocabularies

### 2012-03-11 analysis.tex
structured contents; added TODOs
minor additions

\subsection{Vocabularies}

@@

>>>>

\todo{BH}{make clear that tool also provides reports not only numeric values}

\subsection{Vocabulary Data Set}

\todo{CM}{Add dataset table so that we know how much space this will take.}
\begin{table}[h]
\caption{Analyzed vocabularies}
\begin{tabular}{|p{2.5cm}|p{6cm}|p{2cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|}
\hline
\textbf{Domain} & \textbf{Vocabulary} & \textbf{CO} & \textbf{LR} & \textbf{SR} & \textbf{AR} & \textbf{CS} & \textbf{CL}\\
\hline
Media & GTAA & & & & & & \\
\hline
Science & Geonames Ontology &&&&&& \\
\hline
& MeSH &&&&&& \\
\hline
& Peroxisome Knowledge Base &&&&&& \\
\hline
Government & Eurovoc &&&&&& \\
\hline
& IPSV &&&&&& \\
\hline
\\
\hline

\end{tabular}
\end{table}

@@

\todo{CM}{Add the result table, with one row for the lc metric.}

\todo{CM}{Add result interpretation for this one metric}

### 2012-03-11 introduction.tex
minor additions

% What is SKOS?
The Simple Knowledge Organization System (SKOS) \todo{CM}{reference, no footnote} is a standard model for sharing and linking controlled vocabularies on the Web. Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be accessed and by humans and machines.

@@

% Note: I am still having problems to imagine why and how one would implement query expansion based on the DBPedia categories...as long as this is not clear, better skip the example.

>>>>

% What is SKOS?
The Simple Knowledge Organization System (SKOS) \cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web. Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be accessed and by humans and machines.

@@

% Note: I am still having problems to imagine why and how one would implement query expansion based on the DBPedia categories...as long as this is not clear, better skip the example.
% mein fantasie-szenario ist folgendes: jmd hat einen korpus an dokumenten und will diesen nach kategorien indizieren. also sucht man ein existierendes vocab das man verwenden könnte (irgendwelche subject headings oder eben die dbpedia kategorien weil die eben schon in SKOS verfügbar sind und dbpedia sowieso das zentrum der ld-welt darstellt :). Also verschlagwortet man den dokumentkorpus mit dbpedia-categories und kommt dann, aufgrund der loose concepts drauf, dass dokumente die in ähnliche kategorien (broader/narrower) fallen, nicht gefunden werden können, also den recall verschlechtern. ist das unrealistisch?

### 2012-03-11 main.tex
minor additions

The Simple Knowledge Organization System (SKOS) has become the standard model for expressing and publishing controlled vocabularies on the Web. However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries. Here we investigate how we can support domain experts with quantitative indicators to judge the quality of SKOS vocabularies. We identified existing \textbf{quality criteria} and formalized them into computable \textbf{quality metrics}. We implemented them in the qSKOS quality assessment tool and used it to analyze the quality of existing vocabularies. The results from this analysis indicate that \todo{CM,BH}{summarize results in one sentence}.

@@

\bibliography{lit}
\bibliographystyle{splncs03}

>>>>

The Simple Knowledge Organization System (SKOS) has become the standard model for expressing and publishing controlled vocabularies on the Web. However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries. Here we investigate how we can support domain experts with quantitative indicators to judge the quality of SKOS vocabularies. [cm: Based on existing guidelines and best practices for creating controlled vocabularies, we] We identified existing \textbf{quality criteria} and formalized them into computable \textbf{quality metrics}. We implemented them in the qSKOS quality assessment tool and used it to analyze the quality of existing vocabularies. The results from this analysis indicate that \todo{CM,BH}{summarize results in one sentence}.

@@

\bibliography{references}
\bibliographystyle{splncs03}
